Dynamic Modeling, Parameter Estimation and Uncertainty Analysis in \proglang{R}

### 2016-10-03 article.tex
Xs, what is s?

\pkg{dMod} seeks to stay close to the mathematical formulation, i.e.~\code{x <- Xs(myodemodel)} will indeed return an \proglang{R} function, an object of class \code{prdfn}, which expects arguments \code{times} and \code{pars} and turns them into a model prediction. However, not only the solution $x(t)$ is returned, the sensitivities $\frac{\partial x}{\partial p}(t)$ are returned, too.

@@

Objective functions can be added by the \code{"+"} operator, meaning the objective values, gradients and Hessians are accumulated by summation. Besides the standard function \code{normL2()}, the functions \code{constraintL2()} and \code{datapointL2()} produce objective functions, too. They allow to define parameter priors or treat data points as parameters. Thus, a typical objective function used for parameter estimation could be \code{obj <- normL2(data, g*x*(p1+p2+p3)) + constraintL2(mu, sigma)}.

>>>>

\pkg{dMod} seeks to stay close to the mathematical formulation, i.e.~\code{x <- Xs(myodemodel)} will indeed return an \proglang{R} function, an object of class \code{prdfn}, which expects arguments \code{times} and \code{pars} and turns them into a model prediction. However, as indicated by the \code{"s"} in \code{"Xs"}, not only the solution $x(t)$ is returned, the sensitivities $\frac{\partial x}{\partial p}(t)$ are returned, too.

@@

Objective functions can be added by the \code{"+"} operator, meaning the objective values, gradients and Hessians are accumulated by summation. Besides the standard function \code{normL2()}, the functions \code{constraintL2()} and \code{datapointL2()} produce objective functions, too. They allow to define parameter priors or treat data points as parameters. Thus, a typical objective function used for parameter estimation could be 
\begin{center}
	\code{obj <- normL2(data, g*x*(p1+p2+p3)) + constraintL2(mu, sigma)}.
\end{center}
